\propertitle

### 2019-06-11 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-11T14:46:37+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In the present work we give an answer to this question: What inferences
about the \emph{total activity} of a large neuronal network can we make by
recording a very small sample thereof? We'll first give an answer by
combining, in a straightforward way, the maximum-entropy method and basic
sampling relations of the probability calculus. Later on we'll show that
this answer can be obtained by exclusively using the probability calculus;
this point of view will show that the maximum-entropy answer is a first
approximation of a more complete one, and the assumptions lying behind it.

We apply this method to two concrete data sets:

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-11T15:16:29+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In the present work we give an answer to this question: What inferences
about the \emph{total activity} of a large neuronal network can we make by
recording a very small sample thereof? We'll first give an answer by
combining, in a straightforward way, the maximum-entropy method and basic
sampling relations of the probability calculus. Later on we'll show that
this answer can be obtained by exclusively using the probability calculus;
this point of view shows that the maximum-entropy answer is a first
approximation to the answers of \emph{three} different questions, and also
shows the assumptions lying behind it.

We apply our approach to two concrete data sets: the activity of 65 neurons
recorded from a rat's Medial Entorhinal Cortex \mynote{ref}, and the
activity of 159 neurons recorded from a macaque's Motor Cortex
\mynote{ref}\mynote{add recording length}. In the first data set, the most
interesting inference is that the most probable frequency distribution for
the total activity of the full population, if the latter is assumed to be
larger than 1\,000 neurons, has two very distinct modes, both at low
activities ($0.7\%$ and $2.6\%$ of simultaneously active neurons within
$3\;\mathrm{ms}$, see \fig***). The analogous distribution for second data
set doesn't have two modes but still presents one prominent shoulder in the
low-activity mode. Note that these inferred features for the full
population aren't observed in the sample, nor are they inferred by the
application of maximum-entropy to the sample alone.
